Accounting for uncertainty in simulating greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-19 Manuscript_figures.Rmd
another update

ggsave("figures/Fig_3_scatter_and_surface_per_head_milk_emissions_intensity.png",width=10,height=6)
```

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(breaks = c(0.9),col="black") + theme_bw()

@@

@@

```{r, warning=FALSE, fig.dim = c(8, 4), fig.cap="***Figure S2.*** *Observed distributions of milk yields for all cattle breeds encountered among dairy cows in a survey of livestock-keeping smallholder farms in Kenya.*"}
# breed intervention

@@

ggsave("figures/Fig_S2_breeds.png", width=9,height=4)

@@

```{r}
breed_res<-load_temperature_scenarios("results","Breed_intervention")
class(breed_res)<-"mcSimulation"
nobull_res<-load_temperature_scenarios("results","Nobull_intervention")
class(nobull_res)<-"mcSimulation"
lessReplace_res<-load_temperature_scenarios("results","LessReplace_intervention")
class(lessReplace_res)<-"mcSimulation"
Calliandra_res<-load_temperature_scenarios("results","Calliandra_intervention")
class(Calliandra_res)<-"mcSimulation"
balance_res<-load_temperature_scenarios("results","Balance_intervention")
class(balance_res)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8), fig.cap="***Figure S2.*** *Intervention impact on per head milk production and greenhouse gas emissions intensity.*"}

@@

interventions_scatter<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_6a_intervention_impacts.png", width=9,height=6)

@@

interventions_scatter_relative<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S3.*** *Influence of the breed composition of farm-scale dairy cow populations on changes in milk yield and emissions intensity of milk production in response to a breed upgrade intervention*."}

@@

ggsave("figures/Fig_S3_breed_diagnostics.png",width=8,height=5)

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S4.*** *Influence of the percentage of unproductive bulls in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'retiring unproductive bulls' intervention*."}

@@

ggsave("figures/Fig_S4_nobull_diagnostics.png",width=8,height=5)

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S5.*** *Influence of the percentage of replacement males in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'fewer replacement males' intervention*."}

@@

ggsave("figures/Fig_S5_lessReplace_diagnostics.png",width=8,height=5)

@@

interventions_summary_milk<-data.frame(Intervention=c("Breed upgrade",
                                                 "Retiring unproductive bulls",
                                                 "Fewer replacement males",
                                                 "Calliandra feed",
                                                 "Balanced diet"))
interventions_summary_emissions<-interventions_summary_milk

@@

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S6.*** *Intervention impacts on milk production per head and greenhouse gas emissions intensity, in comparison to random changes between two evaluation times. The gray dots illustrate random changes that occurred on farms that made no management changes, whereas the colored dots show changes on farms that implemented the respective interventions.*"}

@@

interventions_scatter_end<-ggplot(data=normal_plot,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_milk_end,
                        aes(x=milk_change,y=emissions_intensity_change, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention")  +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_7a_intervention_impacts_endline.png", width=9,height=6)

@@

interventions_scatter_relative_end<-ggplot(data=normal_plot,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_milk_end,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

interventions_end_summary_milk<-data.frame(Intervention=c("Breed upgrade",
                                                 "Retiring unproductive bulls",
                                                 "Fewer replacement males",
                                                 "Calliandra feed",
                                                 "Balanced diet",
                                                 "No intervention"))
interventions_end_summary_emissions<-interventions_end_summary_milk

@@

interventions_probability<-ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~at~endline~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~at~baseline~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") +
  stat_contour(aes(z=probability),breaks = c(0.9),col="black") + theme_bw() +
  geom_point(data=int_none_plot,aes(x=pc_milk_baseline,y=pc_milk_yield), size=0.8, color="coral1") +
  ylim(c(0,NA)) + xlim(c(0,NA)) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance","none"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet", "No intervention"))  )

@@

confidence_level_analysis$confidence<-confidence_level_analysis$confidence*100
confidence_plot<-melt(confidence_level_analysis,id.vars = "confidence")
confidence_plot$variable <- factor(confidence_plot$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type2error"),
                  labels = c("Type I error - failure to reward 'Breed upgrade' adopters",
                             "Type I error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type I error - failure to reward 'Fewer replacement males' adopters",
                             "Type I error - failure to reward 'Calliandra feed' adopters",
                             "Type I error - failure to reward 'Balanced diet' adopters",
                             "Type II error - rewarding non-adopters"))

@@

GHG_sim_update<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios_update.csv",
                                                      fileEncoding = "UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 numberOfModelRuns = 10,
                                 functionSyntax = "plainNames")
GHG_sim_update$y[,"CO2eq_per_milk"]<-GHG_sim_update$y$pc_on_farm/GHG_sim_update$y$pc_milk_yield
dir.create("results")
save_temperature_scenarios(GHG_sim_update,"results","Update_better_milk_yield_estimates")

GHG_sim_update_endline<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios_update.csv",
                                                      fileEncoding = "UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 numberOfModelRuns = 10,
                                 functionSyntax = "plainNames")
GHG_sim_update_endline$y[,"CO2eq_per_milk"]<-GHG_sim_update_endline$y$pc_on_farm/GHG_sim_update_endline$y$pc_milk_yield
dir.create("results")
save_temperature_scenarios(GHG_sim_update_endline,"results","Update__endline_better_milk_yield_estimates")

```
```{r}
GHG_sim_update<-load_temperature_scenarios("results","Update_better_milk_yield_estimates")
class(GHG_sim_update)<-"mcSimulation"
GHG_sim_update_endline<-load_temperature_scenarios("results","Update__endline_better_milk_yield_estimates")
class(GHG_sim_update_endline)<-"mcSimulation"

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S7.*** *Probability of a particular farm B featuring lower emissions intensity of milk production than another farm A, based on observed per-head milk production levels, under the assumption that errors in milk yield estimates have been reduced to 15%. Estimates are derived from pairwise comparisons of slices through a population-wide generalization surface of the relationship between per-head milk production and emissions intensity. This generalization was generated through Monte Carlo simulation, based on scenarios representing observed production settings on 414 livestock-keeping smallholder farms in Kenya.*"}

@@

dec_emis_prob_update<-ggplot(data = dec_emiss_update_effects, aes(Base_yield, new_yield, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability of lower emissions intensity on farm B - impact on added precision for milk yield measurements") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(breaks = c(0.9),col="black") + theme_bw() + facet_wrap(~version)

@@

ggsave("figures/Fig_S7_updated_probability_of_lower_emissions_intensity.png", width=10,height=5)

@@

@@

interventions_scatter_end_update<-ggplot(data=normal_stuff,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_stuff,
                        aes(x=milk_change,y=emissions_intensity_change, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed upgrade", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention")  +
  facet_grid(cols=vars(version),
             rows=vars(factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet")))) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_S8_intervention_impacts_endline.png", width=9,height=12)

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S9. *** *Intervention impacts on milk yield and greenhouse gas emissions intensity at an endline sampling point vs. the initial sampling time, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). The colored background surface indicates the probability that increases in milk productivity are associated with decreasing emissions intensity.*"}

@@

interventions_probability_update<-ggplot(data = decreased_emissions_probability_stuff, aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~at~endline~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~at~baseline~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") +
  stat_contour(aes(z=probability),breaks = c(0.9),col="black") + theme_bw() +
  geom_point(data=int_none_plot_stuff,aes(x=pc_milk_baseline,y=pc_milk_yield), size=0.8, color="coral1") +
  ylim(c(0,NA)) + xlim(c(0,NA)) +
  facet_grid(cols=vars(version),
             rows=vars(factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed upgrade", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))))

@@

ggsave("figures/Fig_S9_probability_of_lower_emissions_intensity_interventions.png", width=7,height=12)

@@

```{r, fig.dim = c(8, 12), fig.cap="***Figure S10.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emissions intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of failing to recognize households that implemented interventions, whereas the Type II error represents the percentage of households that did not make any changes, but are nevertheless rewarded due to random effects.*"}

>>>>

ggsave("figures/Fig_3_scatter_and_surface_per_head_milk_emissions_intensity.png",width=10,height=6)

Extracting the LOESS regression from the plot and empirically determining minimum milk yield that would be outside the confidence interval

```{r, warning=FALSE}

prediction_data<-ggplot_build(plot1)$data[[2]]

valuecrowd<-approx(prediction_data$x, y = prediction_data$ymax, xout= seq(100,10000,10), method="linear")

for(i in 1:nrow(prediction_data))
{
  closest<-min(which(valuecrowd$x>prediction_data$x[i] & valuecrowd$y<prediction_data$ymin[i]))
  prediction_data[i,"min_more_milk_loess"]<-valuecrowd$x[closest]
}

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S2.*** *Probability of a particular farm B featuring lower emissions intensity of milk production than another farm A, based on observed per-head milk production levels (see caption to Fig. 5 for more details). The red line indicates a confidence threshold that is based on the 95% confidence interval of the loess regression line shown in Fig. 3a. Using this threshold for predicting changes in emissions intensity based on milk yield data would likely lead to a lot of inaccurate classifications.*"}

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  geom_smooth(data=prediction_data, aes(x=x,y=min_more_milk_loess),col="red")  +  geom_abline(slope=1,intercept=0,linetype = "dashed")  +
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

ggsave("figures/Fig_S2_probability_of_lower_emissions_intensity.png", width=7,height=5)

@@

```{r, warning=FALSE, fig.dim = c(8, 4), fig.cap="***Figure S3.*** *Observed distributions of milk yields for all cattle breeds encountered among dairy cows in a survey of livestock-keeping smallholder farms in Kenya.*"}
# breed intervention

@@

ggsave("figures/Fig_S3_breeds.png", width=9,height=4)

@@

```{r, include=FALSE}
breed_res<-load_temperature_scenarios("results","Breed_intervention")
class(breed_res)<-"mcSimulation"
nobull_res<-load_temperature_scenarios("results","Nobull_intervention")
class(nobull_res)<-"mcSimulation"
lessReplace_res<-load_temperature_scenarios("results","LessReplace_intervention")
class(lessReplace_res)<-"mcSimulation"
Calliandra_res<-load_temperature_scenarios("results","Calliandra_intervention")
class(Calliandra_res)<-"mcSimulation"
balance_res<-load_temperature_scenarios("results","Balance_intervention")
class(balance_res)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8), fig.cap="***Figure S4.*** *Intervention impact on per head milk production and greenhouse gas emissions intensity.*"}

@@

interventions_scatter<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_S4_intervention_impacts.png", width=9,height=6)

@@

interventions_scatter_relative<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S5.*** *Influence of the breed composition of farm-scale dairy cow populations on changes in milk yield and emissions intensity of milk production in response to a breed change intervention*."}

@@

ggsave("figures/Fig_S5_breed_diagnostics.png",width=8,height=5)

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S6.*** *Influence of the percentage of unproductive bulls in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'retiring unproductive bulls' intervention*."}

@@

ggsave("figures/Fig_S6_nobull_diagnostics.png",width=8,height=5)

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S7.*** *Influence of the percentage of replacement males in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'fewer replacement males' intervention*."}

@@

ggsave("figures/Fig_S7_lessReplace_diagnostics.png",width=8,height=5)

@@

interventions_summary_milk<-data.frame(Intervention=c("Breed change",
                                                 "Retiring unproductive bulls",
                                                 "Fewer replacement males",
                                                 "Calliandra feed",
                                                 "Balanced diet"))
interventions_summary_emissions<-interventions_summary_milk

@@

```{r, include=FALSE}

@@

@@

interventions_scatter_end<-ggplot(data=normal_plot,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_milk_end,
                        aes(x=milk_change,y=emissions_intensity_change, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention")  +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_S8_intervention_impacts_endline.png", width=9,height=6)

@@

interventions_scatter_relative_end<-ggplot(data=normal_plot,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_milk_end,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

interventions_end_summary_milk<-data.frame(Intervention=c("Breed change",
                                                 "Retiring unproductive bulls",
                                                 "Fewer replacement males",
                                                 "Calliandra feed",
                                                 "Balanced diet",
                                                 "No intervention"))
interventions_end_summary_emissions<-interventions_end_summary_milk

@@

interventions_probability<-ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~at~endline~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~at~baseline~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") +
  stat_contour(aes(z=probability),breaks = c(0.9),col="black") + theme_bw() +
  geom_point(data=int_none_plot,aes(x=pc_milk_baseline,y=pc_milk_yield), size=0.8, color="coral1") +
  ylim(c(0,NA)) + xlim(c(0,NA)) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance","none"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet", "No intervention"))  ) +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),max(decreased_emissions_probability$Base_yield)),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),max(decreased_emissions_probability$new_yield)),expand = c(0, 0))

@@

confidence_level_analysis$confidence<-confidence_level_analysis$confidence*100
confidence_plot<-melt(confidence_level_analysis,id.vars = "confidence")
confidence_plot$variable <- factor(confidence_plot$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type2error"),
                  labels = c("Type I error - failure to reward 'Breed change' adopters",
                             "Type I error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type I error - failure to reward 'Fewer replacement males' adopters",
                             "Type I error - failure to reward 'Calliandra feed' adopters",
                             "Type I error - failure to reward 'Balanced diet' adopters",
                             "Type II error - rewarding non-adopters"))

@@

GHG_sim_update<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios_update.csv",
                                                      fileEncoding = "UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 numberOfModelRuns = 10,
                                 functionSyntax = "plainNames")
GHG_sim_update$y[,"CO2eq_per_milk"]<-GHG_sim_update$y$pc_on_farm/GHG_sim_update$y$pc_milk_yield
save_temperature_scenarios(GHG_sim_update,"results","Update_better_milk_yield_estimates")

GHG_sim_update_endline<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios_update.csv",
                                                      fileEncoding = "UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 numberOfModelRuns = 10,
                                 functionSyntax = "plainNames")
GHG_sim_update_endline$y[,"CO2eq_per_milk"]<-GHG_sim_update_endline$y$pc_on_farm/GHG_sim_update_endline$y$pc_milk_yield
save_temperature_scenarios(GHG_sim_update_endline,"results","Update_endline_better_milk_yield_estimates")

```
```{r, include=FALSE}
GHG_sim_update<-load_temperature_scenarios("results","Update_better_milk_yield_estimates")
class(GHG_sim_update)<-"mcSimulation"
GHG_sim_update_endline<-load_temperature_scenarios("results","Update_endline_better_milk_yield_estimates")
class(GHG_sim_update_endline)<-"mcSimulation"

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S9.*** *Probability of a particular farm B featuring lower emissions intensity of milk production than another farm A, based on observed per-head milk production levels, under the assumption that errors in milk yield estimates have been reduced to 15%. Estimates are derived from pairwise comparisons of slices through a population-wide generalization surface of the relationship between per-head milk production and emissions intensity. This generalization was generated through Monte Carlo simulation, based on scenarios representing observed production settings on 414 livestock-keeping smallholder farms in Kenya.*"}

@@

dec_emis_prob_update<-ggplot(data = dec_emiss_update_effects, aes(Base_yield, new_yield, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability of lower emissions intensity on farm B - impact on added precision for milk yield measurements") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(breaks = c(0.9),col="black") + theme_bw() + facet_wrap(~version) +
  scale_x_continuous(limits=c(min(dec_emiss_update_effects$Base_yield),max(dec_emiss_update_effects$Base_yield)),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(dec_emiss_update_effects$new_yield),max(dec_emiss_update_effects$new_yield)),expand = c(0, 0))

@@

ggsave("figures/Fig_S9_updated_probability_of_lower_emissions_intensity.png", width=10,height=5)

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S10.*** *Intervention impacts on milk production per head and greenhouse gas emissions intensity, in comparison to random changes between two evaluation times. The gray dots illustrate random changes that occurred on farms that made no management changes, whereas the colored dots show changes on farms that implemented the respective interventions.*"}

@@

interventions_scatter_end_update<-ggplot(data=normal_stuff,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(color="gray",size=1) +
  geom_point(data=interventions_normal_stuff,
                        aes(x=milk_change,y=emissions_intensity_change, color=intervention),size=0.8) +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention")  +
  facet_grid(cols=vars(version),
             rows=vars(factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet")))) +
  theme(legend.position = "none")

@@

ggsave("figures/Fig_S10_intervention_impacts_endline.png", width=9,height=12)

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S11. *** *Intervention impacts on milk yield and greenhouse gas emissions intensity at an endline sampling point vs. the initial sampling time, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). The colored background surface indicates the probability that increases in milk productivity are associated with decreasing emissions intensity.*"}

@@

interventions_probability_update<-ggplot(data = decreased_emissions_probability_stuff, aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~at~endline~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~at~baseline~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") +
  stat_contour(aes(z=probability),breaks = c(0.9),col="black") + theme_bw() +
  geom_point(data=int_none_plot_stuff,aes(x=pc_milk_baseline,y=pc_milk_yield), size=0.8, color="coral1") +
  ylim(c(0,NA)) + xlim(c(0,NA)) +
  facet_grid(cols=vars(version),
             rows=vars(factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))))

@@

ggsave("figures/Fig_S11_probability_of_lower_emissions_intensity_interventions.png", width=7,height=12)

@@

```{r, fig.dim = c(8, 12), fig.cap="***Figure S12.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emissions intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of failing to recognize households that implemented interventions, whereas the Type II error represents the percentage of households that did not make any changes, but are nevertheless rewarded due to random effects.*"}
